\section{Milestones}

%There are two milestone reports in the quarter, one early and one late. These are opportunities for feedback and guidance from staff and classmates.

%Explain what your group will plan to accomplish by each of these milestones. You will be asked to revisit these plans during those milestone reports.

%What might the group explicitly decide to omit?

%Progress requires compromise, as you cannot accomplish everything. Explain what aspects of the project you might choose to ignore or defer in this course. This is your opportunity to scope the project appropriately for this course.

For the first milestone, we expect to complete several paper-mocks of proposed designs of these games (visual and game mechanics) and solicit feedback on how engaging the gameplay will be. We will analyze and iterate over these designs and narrow them down to a subset that we will implement.

For the second milestone, we will implement the designs and mechanisms selected from the first milestone and conduct experiments on Amazon Mechanical Turk (AMT). We will compare tracked user interactions to refine and iterate to find the best game design. Our criteria will include both optimizing subjective enjoyment through surveys and looking at interaction patterns to optimize efficiency and promote user activity.

For omissions, we may decide to omit or defer extensively studying incentive systems. While good incentive systems can allow us to achieve more runs with less cash payment (or potentially no monetary incentives), we think that fine grained iteration on this can be left to future study. Our main focus will also be to compare game mechanics and thus we will also limit exploration in visual tweaking (our task is mostly text based so this is a reasonable compromise).


